---
title       : Stopping Distance
subtitle    : Knowing When to Stop
author      : Matt Frei
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Know When To Stop

When driving, it is important to know how much distance you need to safely stop a car. I've built a simple online tool you can use to estimate how much space you need based on the speed the car is moving.

---

## Example Prediction

The online tools uses a simple linear prediction model shown here. The user inputs a speed and the model estimates the required stopping distance.

Speed = 15 MPH

```{r,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE}
library(datasets)
cars <- cars
mod <- lm(dist~speed,data=cars)
speed <- 15

get.prediction <- function(speed) {
     raw.pred <- predict(mod,newdata = as.data.frame(speed,column.names=c('speed')))
     as.integer(round(raw.pred,2))
}

```
Prediction = `r get.prediction(speed)`

```{r,echo=FALSE,warning=FALSE,error=FALSE,message=FALSE,fig.width=11,fig.height=5,fig.align='center'}
 plot(cars$speed,cars$dist,xlab = 'Speed (MPH)',ylab = 'Stopping Distance (Feet)')
 title('Speed and Stopping Distances')
 abline(mod)
 points(x=speed,y=get.prediction(speed),pch=13,col = 'red',cex=3)
```

---

## Try It Yourself

1. [Online Tool](https://mattfrei.shinyapps.io/Data_Products_Project)

2. [R Code](https://github.com/mattfrei27/DataProducts)

---

## Disclaimer

Note that this analysis is based on data recoded in the 1920s. Also, many other factors, not available in this data set likely affect stopping distance (e.g. vehicle weight).
